Capstone Movielens Report

### 2025-12-23 reports/capstone-movielens.site/02-3.OMR-model.Rmd
Fix for code chunk (duplicate name) in report section: OMR Model

We can now calculate the *Root Mean Squared Error (RMSE)* for the current model as a *square root* of the average of the *MSE* values we obtained above, using the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L117):
```{r main-script@l110 }
mu.RMSE <- sqrt(mean(mu.MSEs))
mu.RMSE
```

>>>>

We can now calculate the *Root Mean Squared Error (RMSE)* for the current model as a *square root* of the average of the *MSE* values we obtained above, using the following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L117):
```{r main-script@l117 }
mu.RMSE <- sqrt(mean(mu.MSEs))
mu.RMSE
```
